Propositions as Sessions, Mechanically

### 2015-04-22 paper/presentation.tex
I have some more ideas on how to proceed (script and slide-wise).

\usepackage[latin1]{inputenc}
\usepackage{lstmacros}
\usepackage{graphicx}
\usepackage{array}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{etoolbox}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage[style=alphabetic,natbib=true]{biblatex}

@@

@@

@@

\begin{frame}
\frametitle{Session Types}
\begin{math}
  \begin{array}{rclc}
    S & \bnf  & \inpt{T}{S} & \mbox{input value of type T, continue as S}\\
      & \altt & \outpt{T}{S} & \mbox{output value of type T, continue as S}\\
      & \altt & \Branch{l_i}{S_i}{i\in I} &
                           \mbox{offer between $i$ alternatives}\\
      & \altt & \Choice{l_i}{S_i}{i\in I} &
                           \mbox{choose between $i$ alternatives}\\
      & \altt & \mbox{\lstinline{end}} & \mbox{terminate session}
 \end{array}
\end{math}
\end{frame}

@@

\begin{frame}
Hand-written (informal) proofs $=$ Error-prone $+$ Difficult to update
\end{frame}

@@

\begin{frame}
CP - process calculus with operators from classical linear logic
GV - functional language with session type
CP -> GV translation (interprets classical linear logic operators as session
types)
\end{frame}

@@

\begin{frame}
negation as involution
an example of CP classical linear logic operators and their session type
interpretation (times/with)
\end{frame}

@@

@@

\begin{frame}
\frametitle{Preamble}
\begin{itemize}
\item Propositions as Sessions
\item system features
\item Coq
\item encoding
\item subject reduction theorem
\item difficulties in formalisation
\item implications
\item future work
\end{itemize}
\end{frame}

>>>>

\usepackage[latin1]{inputenc}
\usepackage{cmll}
\usepackage{lstmacros}
\usepackage{graphicx}
\usepackage{array}
\usepackage{subfigure}
\usepackage{amsmath}
\usepackage{comment}
\usepackage{etoolbox}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning}
\usepackage[style=alphabetic,natbib=true]{biblatex}

@@

\let\oldframetitle\frametitle
\renewcommand{\frametitle}[1]{
  \oldframetitle{#1}\vspace{-3.5cm}
}

@@

\section{Preamble}

@@

\begin{frame}
\oldframetitle{Session Types}
\begin{math}
  \begin{array}{cccc}
    S & \bnf  & \inpt{T}{S} & \mbox{receive value of type T, continue as S}\\
      & \altt & \outpt{T}{S} & \mbox{send value of type T, continue as S}\\
      & \altt & \Branch{l_i}{S_i}{i\in I} &
                           \mbox{offer between $|I|$ alternatives}\\
      & \altt & \Choice{l_i}{S_i}{i\in I} &
                           \mbox{choose between $|I|$ alternatives}\\
      & \altt & \mbox{\lstinline{end}} & \mbox{terminate session}\\
 \dual{S} & \bnf & \mbox{dual of S}\\
 \dual{(\inpt{T}{S})} & \bnf & \outpt{T}{\dual{S}}\\
 \dual{\Branch{l_i}{S_i}{i\in I}} & \bnf & \Choice{l_i}{\dual{S_i}}{i\in I}\\
            \vdots                & \cdots & \vdots
 \end{array}
\end{math}
\end{frame}

@@

\begin{frame}
\frametitle{Motivation}
Hand-written (informal) proofs $=$ Error-prone $+$ Difficult to update
\end{frame}

@@

\begin{frame}
\frametitle{System Overview}
CP $=$ process calculus with operators from classical linear logic

GV $=$ functional language with session types

GV $\to$ CP translation
\end{frame}

@@

\begin{frame}
\frametitle{CP Propositions}
\begin{math}
\begin{array}{rclc}
    \tp{A,B,C} & \bnf
          & \tp{A \otimes B} & \key{times: output A then behave as B}\\
          & \altt & \tp{A \parr B} & \key{par: input A then behave as B}\\
          & \altt & \cdots
\end{array}
\end{math}

For all propositions $A$, $\dualbt{(\dualbt{A})} = A$ (negation is an
involution)
\end{frame}

@@

\section{Formalisation}

\begin{frame}
\frametitle{Goals}
\begin{itemize}
\item Reuse where possible
\item Minimise difference between informal/formal variants
\item Avoid known pitfalls
\end{itemize}
\end{frame}

\begin{comment}
The encoding follows practices in formalising programming language metatheory
with a principal design goal of reusing existing libraries from previous
developments. Additionally, I want to keep as close a correspondence as
possible between the development and the pen-and-paper presentation in order
to mitigate questions of adequacy, you know, whether the formal system is what
you intended to formalise. And lastly, I aimed to exploit the features of the
Coq system without over complicating the development such as taking careful
consideration over representation choices.
\end{comment}

\begin{frame}
\oldframetitle{Preliminaries}
\begin{itemize}
\item Locally Nameless
  \begin{itemize}
  \item Avoids variable capture
  \item de Bruijn indices for bound variables
    ($\lambda~(\lambda~1) \equiv \lambda x. \lambda y. x$)
  \end{itemize}
\item Cofinite Quantification
  \begin{itemize}
  \item stronger induction principle
  \item
    \begin{math}
    \begin{array}{lcl}
      \mbox{Exists-Fresh} & & \mbox{Cofinite}\\
      \inference{
        x \notin FV(N) &
        \Tp{\Gamma \comma \Tmof{x}T} \Tpvdash \Tmof{N^x}\Tp{U}
      }{}{
        \Tp{\Gamma} \Tpvdash \Tmof{abs~N}\Tp{T \to U}
      }
    & \mbox{vs}. &
      \inference{
        \forall x \notin L.
        (\Tp{\Gamma \comma \Tmof{x}T} \Tpvdash \Tmof{N^x}\Tp{U})
      }{}{
        \Tp{\Gamma} \Tpvdash \Tmof{abs~N}\Tp{T \to U}
      }
    \end{array}
    \end{math}
  \end{itemize}
\item Metatheory library for representation
\end{itemize}
\end{frame}

\begin{comment}
one of the key issues when formalising programming language metatheory is how
to represent variables both bound and free. I chose the locally nameless
representation which separates bound and free variables into distinct
entities. Thus it avoids the variable capture problem in contrast to other
approaches.

In this approach, a de Bruijn index is a number used to represent a bound
variable which indicates the position of its binder (starting from zero for
the innermost binder).

Constructs with binders have to open the term with a free variable and this
requires some technique for handling freshness of the opening variable. I
chose to adopt the cofinite quantification approach which allows to exclude a
finite set of names from consideration. in contrast to the sometimes weaker
notion of a single sufficiently fresh name
\end{comment}

\begin{frame}
another frame for cp this time its well typing time
\end{frame}

\begin{comment}
lets take a look at cp's typing rules. here we used a well typed relation on
the process terms of cp. we require additional assumptions for environment
ordering and
\end{comment}

@@

\begin{frame}
\begin{itemize}
\item Propositions as Sessions
\item system features
\item Coq
\item encoding
\item subject reduction theorem
\item difficulties in formalisation
\item implications
\item future work
\end{itemize}
\end{frame}
